Supplemental material

### 2024-08-30 supplemental_material.Rmd
new code for plotting and model fitting with truncation

# mean BRT for critcality
sm_fig_1_1 <- ggplot(brt_stat_grouped_ttc[["data"]] %>%
         dplyr::mutate(ttc_criticality_factor = as.factor(group)), mapping = aes(value)) +
  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
  geom_vline(response.vehicle.eye %>% 
               dplyr::group_by(ttc_criticality_factor) %>%
               dplyr::summarise(mean_brt = mean(rt)), mapping = aes(xintercept = mean_brt, fill = "T(y)"), col = "darkblue", size = 2) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
  scale_x_continuous(limits = c(1.0, 1.5), breaks = seq(1.0, 1.4, .1), labels = label_number(accuracy = 0.1)) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("A") +
  ylab(" ") +
  xlab(expression(RT[B]~ "(s)")) +
  theme_bw() +
  theme(legend.position = c(.593, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

@@

sm_fig1 <- sm_fig_1_1 / sm_fig_1_2

@@

sm_fig2_1 <- ggplot() + 
  geom_density(yrep_brt, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
  geom_density(response.vehicle.eye, mapping = aes(rt, col = "y"), size = 1) +
  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  xlim(0, 5) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("A") +
  ylab(" ") +
  xlab(expression(RT[B]~ "(s)")) +
  theme_bw() +
  theme(legend.position = c(.94, .69), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

@@

sm_fig2 <- sm_fig2_1 / sm_fig2_2

@@

ggplot(brt_hist[["data"]], mapping = aes(value)) +
  geom_histogram() +
  facet_wrap(~ rep_id)
```

>>>>

# mean BRT for critcality
sm_fig_1_1 <- ggplot(brt_stat_grouped_ttc[["data"]] %>%
         dplyr::mutate(ttc_criticality_factor = as.factor(group)), mapping = aes(value)) +
  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
  geom_vline(response.vehicle.eye %>% 
               dplyr::group_by(ttc_criticality_factor) %>%
               dplyr::summarise(mean_brt = mean(rt)), mapping = aes(xintercept = mean_brt, fill = "T(y)"), col = "darkblue", size = 2) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
  scale_x_continuous(limits = c(1.0, 1.5), breaks = seq(1.0, 1.4, .1), labels = label_number(accuracy = 0.1)) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("A") +
  ylab(" ") +
  xlab(expression(RT[B]~ "(s)")) +
  theme_bw() +
  theme(legend.position = c(.585, .70), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

@@

sm_fig1 <- sm_fig_1_1 / sm_fig_1_2 + plot_layout(axes = "collect")

@@

sm_fig2_1 <- ggplot() + 
  geom_density(yrep_brt, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
  geom_density(response.vehicle.eye, mapping = aes(rt, col = "y"), size = 1) +
  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  xlim(0, 5) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("A") +
  ylab(" ") +
  xlab(expression(RT[B]~ "(s)")) +
  theme_bw() +
  theme(legend.position = c(.94, .71), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

@@

sm_fig2 <- sm_fig2_1 / sm_fig2_2 + plot_layout(axes = "collect")

@@

brt_hist_df <- brt_hist[["data"]] %>%
  mutate(across(everything(), ~ replace_na(., 12)))

sim_labs <- c(seq(1, 11, 1), "Observed data")
names(sim_labs) <- c(seq(1, 11, 1), 12)

sm_fig3 <- ggplot(brt_hist_df, mapping = aes(value, fill = is_y_label)) +
  geom_histogram(col = "black") +
  scale_fill_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ rep_id, labeller = labeller(rep_id = sim_labs)) +
  xlim(0, 5) +
  scale_y_continuous(expand = c(0, 0)) +
  ylab(" ") +
  xlab(expression(RT[B]~ "(s)")) +
  theme_bw() +
  theme(legend.position = c(.945, .905), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig3.tiff"), plot = sm_fig3, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
```

## Hands on reatcion time

```{r}
# loading model
hands_on_rt_model <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/handson_rt_shifted_lognormal_maximal.rds"))

# posterior predictive checks
hort_stat_grouped_ttc <- pp_check(hands_on_rt_model, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
hort_stat_grouped_nback <- pp_check(hands_on_rt_model, type = "stat_grouped", stat = "mean", group = "n_back")

# mean HORT for critcality
sm_fig_4_1 <- ggplot(hort_stat_grouped_ttc[["data"]] %>%
         dplyr::mutate(ttc_criticality_factor = as.factor(group)), mapping = aes(value)) +
  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
  geom_vline(response.vehicle.eye %>% 
               dplyr::group_by(ttc_criticality_factor) %>%
               dplyr::summarise(mean_hort = mean(ho.rt)), mapping = aes(xintercept = mean_hort, fill = "T(y)"), col = "darkblue", size = 2) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
  scale_x_continuous(limits = c(1.1, 1.8), breaks = seq(1.1, 1.8, .2), labels = label_number(accuracy = 0.1)) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("A") +
  ylab(" ") +
  xlab(expression(RT[HO]~ "(s)")) +
  theme_bw() +
  theme(legend.position = c(.593, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

# mean BRT for N-back
sm_fig_4_2 <- ggplot(hort_stat_grouped_nback[["data"]] %>%
         dplyr::mutate(n_back = as.factor(group)), mapping = aes(value)) +
  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
  geom_vline(response.vehicle.eye %>% 
               dplyr::group_by(n_back) %>%
               dplyr::summarise(mean_hort = mean(ho.rt)), mapping = aes(xintercept = mean_hort, fill = "T(y)"), col = "darkblue", size = 2) +
  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
  scale_x_continuous(limits = c(1.1, 1.8), breaks = seq(1.1, 1.8, .2), labels = label_number(accuracy = 0.1)) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("B") +
  ylab(" ") +
  xlab(expression(RT[HO]~ "(s)")) +
  theme_bw() +
  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

sm_fig4 <- sm_fig_4_1 / sm_fig_4_2 + plot_layout(axes = "collect")

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig4.tiff"), plot = sm_fig4, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')

pp_check(hands_on_rt_model, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
pp_check(hands_on_rt_model, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

yrep_hort <- response.vehicle.eye %>% 
  select(ho.rt, n_back, ttc_criticality_factor, ppid) %>% 
  add_predicted_draws(hands_on_rt_model, ndraws = 100)

sm_fig5_1 <- ggplot() + 
  geom_density(yrep_hort, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
  geom_density(response.vehicle.eye, mapping = aes(rt, col = "y"), size = 1) +
  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  xlim(0, 8) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("A") +
  ylab(" ") +
  xlab(expression(RT[HO]~ "(s)")) +
  theme_bw() +
  theme(legend.position = c(.94, .69), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

sm_fig5_2 <- ggplot() + 
  geom_density(yrep_hort, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
  geom_density(response.vehicle.eye, mapping = aes(rt, col = "y"), size = 1) +
  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
  xlim(0, 8) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("B") +
  ylab(" ") +
  xlab(expression(RT[HO]~ "(s)")) +
  theme_bw() +
  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

sm_fig5 <- sm_fig5_1 / sm_fig5_2 + plot_layout(axes = "collect")

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig5.tiff"), plot = sm_fig5, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')

# - change NA to observed data - then use legend to identify y versus y_rep
hort_hist <- pp_check(hands_on_rt_model, type = "hist", ndraws = 11)

hort_hist_df <- hort_hist[["data"]] %>%
  mutate(across(everything(), ~ replace_na(., 12)))

sim_labs <- c(seq(1, 11, 1), "Observed data")
names(sim_labs) <- c(seq(1, 11, 1), 12)

sm_fig6 <- ggplot(hort_hist_df, mapping = aes(value, fill = is_y_label)) +
  geom_histogram(col = "black") +
  scale_fill_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ rep_id, labeller = labeller(rep_id = sim_labs)) +
  xlim(0, 8) +
  scale_y_continuous(expand = c(0, 0)) +
  ylab(" ") +
  xlab(expression(RT[HO]~ "(s)")) +
  theme_bw() +
  theme(legend.position = c(.945, .905), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig6.tiff"), plot = sm_fig6, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
```

## Mean deceleration

```{r}
# loading model
mean_decel_model <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/mean_decel_skewnormal_reg_priors_maximal.rds"))

# posterior predictive checks
decel_stat_grouped_ttc <- pp_check(mean_decel_model, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
decel_stat_grouped_nback <- pp_check(mean_decel_model, type = "stat_grouped", stat = "mean", group = "n_back")

# mean decel for critcality
sm_fig_7_1 <- ggplot(decel_stat_grouped_ttc[["data"]] %>%
         dplyr::mutate(ttc_criticality_factor = as.factor(group)), mapping = aes(value)) +
  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
  geom_vline(response.vehicle.eye %>% 
               dplyr::group_by(ttc_criticality_factor) %>%
               dplyr::summarise(mean_decel = mean(mean_decel)), mapping = aes(xintercept = mean_decel, fill = "T(y)"), col = "darkblue", size = 2) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
  scale_x_continuous(limits = c(-4, -1), breaks = seq(-1, -4, -1), labels = label_number(accuracy = 0.1)) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("A") +
  ylab(" ") +
  xlab(expression(M[D] ~"("~m/s^2~")")) +
  theme_bw() +
  theme(legend.position = c(.593, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

# mean BRT for N-back
sm_fig_7_2 <- ggplot(decel_stat_grouped_nback[["data"]] %>%
         dplyr::mutate(n_back = as.factor(group)), mapping = aes(value)) +
  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
  geom_vline(response.vehicle.eye %>% 
               dplyr::group_by(n_back) %>%
               dplyr::summarise(mean_decel = mean(mean_decel)), mapping = aes(xintercept = mean_decel, fill = "T(y)"), col = "darkblue", size = 2) +
  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
  scale_x_continuous(limits = c(-3, -1.75), breaks = seq(-3, -2, .25), labels = label_number(accuracy = 0.1)) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("B") +
  ylab(" ") +
  xlab(expression(M[D] ~"("~m/s^2~")")) +
  theme_bw() +
  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

sm_fig7 <- sm_fig_7_1 / sm_fig_7_2 + plot_layout(axes = "collect")

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig7.tiff"), plot = sm_fig7, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')

pp_check(mean_decel_model, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
pp_check(mean_decel_model, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

yrep_decel <- response.vehicle.eye %>% 
  select(mean_decel, n_back, ttc_criticality_factor, ppid) %>% 
  add_predicted_draws(mean_decel_model, ndraws = 100)

sm_fig8_1 <- ggplot() + 
  geom_density(yrep_decel, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
  geom_density(response.vehicle.eye, mapping = aes(mean_decel, col = "y"), size = 1) +
  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  #xlim(-9, 2) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("A") +
  ylab(" ") +
  xlab(expression(M[D] ~"("~m/s^2~")")) +
  theme_bw() +
  theme(legend.position = c(.94, .69), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

sm_fig8_2 <- ggplot() + 
  geom_density(yrep_decel, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
  geom_density(response.vehicle.eye, mapping = aes(mean_decel, col = "y"), size = 1) +
  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
  #xlim(-9, 2) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("B") +
  ylab(" ") +
  xlab(expression(M[D] ~"("~m/s^2~")")) +
  theme_bw() +
  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

sm_fig8 <- sm_fig8_1 / sm_fig8_2 + plot_layout(axes = "collect")

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig8.tiff"), plot = sm_fig8, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')

# - change NA to observed data - then use legend to identify y versus y_rep
decel_hist <- pp_check(mean_decel_model, type = "hist", ndraws = 11)

decel_hist_df <- decel_hist[["data"]] %>%
  mutate(across(everything(), ~ replace_na(., 12)))

sim_labs <- c(seq(1, 11, 1), "Observed data")
names(sim_labs) <- c(seq(1, 11, 1), 12)

sm_fig9 <- ggplot(decel_hist_df, mapping = aes(value, fill = is_y_label)) +
  geom_histogram(col = "black") +
  scale_fill_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ rep_id, labeller = labeller(rep_id = sim_labs)) +
  #xlim(-8.5, 1) +
  scale_y_continuous(expand = c(0, 0)) +
  ylab(" ") +
  xlab(expression(M[D] ~"("~m/s^2~")")) +
  theme_bw() +
  theme(legend.position = c(.815, .905), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig9.tiff"), plot = sm_fig9, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
```

## Mean lateral accelerations

```{r}
# loading model
lat_model <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/mean_lat_acc_lognormal_maximal.rds"))

# posterior predictive checks
lat_stat_grouped_ttc <- pp_check(lat_model, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
lat_stat_grouped_nback <- pp_check(lat_model, type = "stat_grouped", stat = "mean", group = "n_back")

### STAT GROUPED PLOTS FOR MEAN lat

# mean lateral for criticality
sm_fig_10_1 <- ggplot(lat_stat_grouped_ttc[["data"]] %>%
         dplyr::mutate(ttc_criticality_factor = as.factor(group)), mapping = aes(value)) +
  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
  geom_vline(response.vehicle.eye %>% 
               dplyr::group_by(ttc_criticality_factor) %>%
               dplyr::summarise(lat = mean(mean_lat_acc)), mapping = aes(xintercept = lat, fill = "T(y)"), col = "darkblue", size = 2) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
  scale_x_continuous(limits = c(.1, .4), breaks = seq(.1, .4, .1), labels = label_number(accuracy = 0.1)) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("A") +
  ylab(" ") +
  xlab(expression(M[LA] ~"("~m/s^2~")")) +
  theme_bw() +
  theme(legend.position = c(.593, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

# mean lateral for N-back
sm_fig_10_2 <- ggplot(lat_stat_grouped_nback[["data"]] %>%
         dplyr::mutate(n_back = as.factor(group)), mapping = aes(value)) +
  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
  geom_vline(response.vehicle.eye %>% 
               dplyr::group_by(n_back) %>%
               dplyr::summarise(lat = mean(mean_lat_acc)), mapping = aes(xintercept = lat, fill = "T(y)"), col = "darkblue", size = 2) +
  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
  scale_x_continuous(limits = c(.1, .4), breaks = seq(.1, .4, .1), labels = label_number(accuracy = 0.1)) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("B") +
  ylab(" ") +
  xlab(expression(M[LA] ~"("~m/s^2~")")) +
  theme_bw() +
  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

sm_fig10 <- sm_fig_10_1 / sm_fig_10_2 + plot_layout(axes = "collect")

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig10.tiff"), plot = sm_fig10, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')

pp_check(lat_model, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
pp_check(lat_model, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

yrep_lat <- response.vehicle.eye %>% 
  select(mean_lat_acc, n_back, ttc_criticality_factor, ppid) %>% 
  add_predicted_draws(lat_model, ndraws = 100)

sm_fig11_1 <- ggplot() + 
  geom_density(yrep_lat, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
  geom_density(response.vehicle.eye, mapping = aes(mean_lat_acc, col = "y"), size = 1) +
  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  xlim(0, 3) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("A") +
  ylab(" ") +
  xlab(expression(M[LA] ~"("~m/s^2~")")) +
  theme_bw() +
  theme(legend.position = c(.94, .69), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

sm_fig11_2 <- ggplot() + 
  geom_density(yrep_lat, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
  geom_density(response.vehicle.eye, mapping = aes(mean_lat_acc, col = "y"), size = 1) +
  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
  xlim(0, 3) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("B") +
  ylab(" ") +
  xlab(expression(M[LA] ~"("~m/s^2~")")) +
  theme_bw() +
  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

sm_fig11 <- sm_fig11_1 / sm_fig11_2 + plot_layout(axes = "collect")

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig11.tiff"), plot = sm_fig11, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')

# - change NA to observed data - then use legend to identify y versus y_rep
lat_hist <- pp_check(lat_model, type = "hist", ndraws = 11)

lat_hist_df <- lat_hist[["data"]] %>%
  mutate(across(everything(), ~ replace_na(., 12)))

sim_labs <- c(seq(1, 11, 1), "Observed data")
names(sim_labs) <- c(seq(1, 11, 1), 12)

sm_fig12 <- ggplot(lat_hist_df, mapping = aes(value, fill = is_y_label)) +
  geom_histogram(col = "black") +
  scale_fill_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ rep_id, labeller = labeller(rep_id = sim_labs)) +
  scale_x_continuous(limits = c(0, 2), breaks = seq(0, 1.5, .5), labels = label_number(accuracy = 0.1)) +
  scale_y_continuous(expand = c(0, 0)) +
  ylab(" ") +
  xlab(expression(M[LA] ~"("~m/s^2~")")) +
  theme_bw() +
  theme(legend.position = c(.945, .905), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

  # plot saving
  ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig12.tiff"), plot = sm_fig12, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
```

## SDLP

```{r}
# loading model
sdlp_model <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/sdlp_lognormal_maximal.rds"))

# posterior predictive checks
sdlp_stat_grouped_ttc <- pp_check(sdlp_model, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
sdlp_stat_grouped_nback <- pp_check(sdlp_model, type = "stat_grouped", stat = "mean", group = "n_back")

### STAT GROUPED PLOTS FOR MEAN SDLP
